Supporting information: Tail associations and their impact on extinction risk

### 2019-11-06 SuppMat.Rmd

<!--moderate tail association noise-->
Bivarite environmental noise with moderate left-tail association (as in Fig. \ref{MT-fig_intro_cop}B) was 
generated using a 2-dimensional Clayton copula. The statistical
theory of copulas has been introduced systematically in several texts 
(e.g., @nelsen2006_copula; @joe2014_dependence), and was briefly 
introduced by @Genest2007. Short, conceptual introductions aimed at ecological
audiences were provided by sections within the papers of @Anderson2018 and @Ghosh_copula. A
2-dimensional Clayton copula is equivalent to a particular bivariate 
probability density function with marginal distributions which are 
uniform on the interval $(0,1)$. The points on Fig. 
\ref{MT-fig_intro_cop}B were independent draws from the associated random variable.
The functions `claytonCopula` and `rCopula` from the `copula` package for the 
R programming language were used. The parameter of the Clayton family was
chosen so that the Spearman correlation was `r srho_common`, the same as that of the
extreme left-tail associated noise. This was accomplished with the `iRho`
function of the `copula` package. Noise with moderate right-tail
association was generated in a similar way but using the 2-dimensional 
survival Clayton copula.
<!--***DAN: Shyamolina, in response to your comment in the pdf, what you
did is mathematically equivalent to this, so OK to say it this way. I added a 
bit of explanation of what that survival Clayon is. Please delete this
comment once you have read it.-->
The survival Clayton copula is a rotation of the Clayton copula by 180 degrees.

>>>>

<!--moderate tail association noise-->
Bivarite environmental noise with moderate left-tail association (as in Fig. \ref{MT-fig_intro_cop}B) was 
generated using a 2-dimensional Clayton copula. The statistical
theory of copulas has been introduced systematically in several texts 
(e.g., @nelsen2006_copula; @joe2014_dependence), and was briefly 
introduced by @Genest2007. Short, conceptual introductions aimed at ecological
audiences were provided by sections within the papers of @Anderson2018 and @Ghosh_copula. A
2-dimensional Clayton copula is equivalent to a particular bivariate 
probability density function with marginal distributions which are 
uniform on the interval $(0,1)$. The points on Fig. 
\ref{MT-fig_intro_cop}B were independent draws from the associated random variable.
The functions `claytonCopula` and `rCopula` from the `copula` package for the 
R programming language were used. The parameter of the Clayton family was
chosen so that the Spearman correlation was `r srho_common`, the same as that of the
extreme left-tail associated noise. This was accomplished with the `iRho`
function of the `copula` package. Noise with moderate right-tail
association was generated in a similar way but using the 2-dimensional 
survival Clayton copula. The survival Clayton copula is a rotation
of the Clayton copula by 180 degrees.
